\documentclass[12pt]{article}
\setlength\parindent{0pt}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }


\begin{document}
\title{ECE-210B Syllabus}
\date{}
\author{Instructor: Cory Nezin}
\maketitle

\textbf{Meeting Time:} Wednesday, 6PM - 7PM \\
\textbf{Room:} 806 \\
\textbf{Email:} ccnezin+ece210@gmail.com

\textbf{Course Overview:}\\
The course material for ECE-210 is a general survey of MATLAB as a pro
gramming language, specifically tailored but not limited to its applications in the realm of signals
processing. Signals and Systems is a corequisite in the sense that the material from ECE-210 is
necessary to perform well in that course, but no substantial knowledge from Signals and Systems
is expected of students in ECE-210.\\

This course is 0 credits and your final grade will be Pass or Fail. Nine homeworks will be assigned
nearly one each week of the semester. Homeworks are to be submitted by email to ccnezin+ece210@gmail.com
as .m files by 11:59 PM the Wednesday after they are assigned unless otherwise stated.\\

\textbf{Grading}\\
Each assignment will award you 0, 1, or 2 points. \\

A 0 is assigned if the homework is not handed in at all or if it does not run. \\

A 1 is assigned if the homework is handed in with many incorrect answers, bad style, or if it is late\\

a 2 is assigned if the homework runs correctly (for the most part), has good style, and is handed in on time.\\

Homeworks may be resubmitted for a new grade at any time.\\

You will lose one point for being absent to a class, if you don't discuss it with me first.\\

You must accumulate a grade of 11 or more to pass this class.\\

\textbf{Contact}\\
Any questions regarding the homeworks or lecture may be emailed to me at any time.
MATLAB inquiries may be made of Brian Forst and Brenda So, the instructors of the other two
sections of ECE-210, as well. Face-to-face tutoring may be offered through the Electrical Engineering department, appointments for which can be made by emailing me. Questions regarding
Signals and Systems may be directed towards myself as well, although they are often better left for
Professor Fontaine. If I do not respond to an email in apt time, chances are that I am not ignoring
you. Please just email me again!
All course materials, including homeworks and lessons will be uploaded to my Github https://github.com/corynezin and my website http://ee.cooper.edu/\textasciitilde nezin/

\end{document}
